---
title: ""
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

self_contained: false

css: zme_style1.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:HoneyDew;
    	cursor: url('/Users/zoeervolino/Documents/zoe/cursor.cur'), default;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(embedr)
library(vembedr)
library(tinytex)
library(emo)
library(rmdprotectr)
library(rmarkdown)
```

<font size=80>
<h1 style=>
`r emo::ji("dizzy")`ZME`r emo::ji("dizzy")`
</h1>
</font>

```{r image1, echo=FALSE, out.width="100%", fig.align='center'}

fruta <- "cartagena/07530025.JPG"
knitr::include_graphics(fruta)

```

<h2>ZOE MORALES ERVOLINO</h2> <h3> is a person doing person things. Enjoy the film photography she captured during her recent voyages to the Colombian coastal cities of Cartagena, Barranquilla, and the nearby island of San Andres.</h3>

<br>
<b><center>   1. Mercado de Bazurto</center>
```{r image2, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530023.JPG"
knitr::include_graphics(a)

```
<br>
<center>    2. Mangostino</center>

```{r image3, echo=FALSE, out.width="70%", fig.align='center'}

a <- "cartagena/07530022.JPG"
knitr::include_graphics(a)

```
<br>

<center>    3. Bazurto</center>
```{r image4, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530021.JPG"
knitr::include_graphics(a)

```
<br>

 <center>   4. Almuerzo Estilo Caleño</center>
```{r image5, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530020.JPG"
knitr::include_graphics(a)

```
<br>

<center>  5. Centro Comercial La Castellana</center>

```{r image6, echo=FALSE, out.width="70%", fig.align='center'}

a <- "cartagena/07530012.JPG"
knitr::include_graphics(a)

```

<br>

  <center>6. Carnicería</center>
```{r image7, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530017.JPG"
knitr::include_graphics(a)

```
<br>

<center>7. Mar "Rojo" de Galarzamba</center>
```{r image8, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530015.JPG"
knitr::include_graphics(a)

```
<br>

<center>8. Mar "Rojo" de Galarzamba</center>
```{r image9, echo=FALSE, out.width="70%", fig.align='center'}

a <- "cartagena/07530014.JPG"
knitr::include_graphics(a)

```
<br>

  <center>9. Ventana al Mundo, Barranquilla, Colombia</center>
```{r image10, echo=FALSE, out.width="70%", fig.align='center'}

a <- "cartagena/07530013.JPG"
knitr::include_graphics(a)

```
<br>

  <center>10. Playa de Boca Grande</center>
```{r image11, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530018.JPG"
knitr::include_graphics(a)

```
<br>

  <center>11. Playa de San Andres</center>
```{r image12, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530011.JPG"
knitr::include_graphics(a)

```
<br>

  <center>12. Playa de San Andres</center>
```{r image13, echo=FALSE, out.width="70%", fig.align='center'}

a <- "cartagena/07530009.JPG"
knitr::include_graphics(a)

```
<br>

  <center>13. Fritanga</center>
```{r image14, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530008.JPG"
knitr::include_graphics(a)

```
<br>

  <center>14. Playa Isla de Jhonny Cay</center>
```{r image15, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530007.JPG"
knitr::include_graphics(a)

```
<br>

  <center>15. Almuerzo Corriente de 7 Mil Pesos</center>
```{r image16, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530002.JPG"
knitr::include_graphics(a)

```

<br>

  <center>16. Las Fruticas de la Calle</center>
```{r image17, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530003.JPG"
knitr::include_graphics(a)

```
<br>

  <center>17. El Malecón de San Andres</center>
```{r image18, echo=FALSE, out.width="70%", fig.align='center'}

a <- "cartagena/07530004.JPG"
knitr::include_graphics(a)

```
<br>

  <center>18. Azoteas de Cartagena</center>
```{r image19, echo=FALSE, out.width="100%", fig.align='center'}

a <- "cartagena/07530001.JPG"
knitr::include_graphics(a)

```
<br></b>